\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement \\ Mini-Arcade \\{\large Lab 1, Team \#4, Mini-Arcade}}

\author{Andrew Hum \\ huma3 \\ 400138826 \and
		William Lei \\ leim5 \\ 400125240 \and
		Arshan Khan \\ khana172 \\ 400145605 \and
		Jame Tran \\ tranj52 \\ 000000000
}

\date{January 24, 2019}

% \input{../Comments} %Cannot find a comments file in the parent directory

\begin{document}
\maketitle
\newpage

\tableofcontents
\newpage



\begin{table}[hp]
\section{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\hline
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\hline
1/21/2020 & Andrew Hum & Initialization \& Rough Ideas.\\
\hline
1/22/2020 & Andrew Hum  & Document Formatting.\\
\hline
1/22/2020 & Arshan Khan & Document Formatting.\\
\hline
1/22/2020 & Andrew Hum & Completed initial draft with a thorough edit. \\
\hline
... & ... & ...\\
\hline
\end{tabularx}
\end{table}

\newpage

\section{Problem Statement}
\subsection{What is the problem to be solved?}
The purpose of any game is to entertain the user. However, the term entertain is broad with many interpretations and meanings based on each individual. Our team believes that the core purpose of a good game is to bring joy to the players, leaving them with a desire to play longer. We believe a game should be easily accessible, pose a challenge to the user to provide a feeling of accomplishment when overcome and be aesthetically pleasing in terms of graphics and performance. The selections of mini-games we currently have are simple with minimal functionality, leaving a minimal desire for the user to play.

\subsection{Why is this problem important?}
The mini-games in their current state do not meet the criteria we previously established to improve user enjoyability. Firstly, the games are difficult to launch, decreasing the appeal to play them. Alongside the difficulty to access, the mini-games have minimal functionality, no difficulty to complete and poor overall performance. These aspects cause the interest factor of the player to exhaust rapidly; in other words, the games in their current state are not entertaining and are not enjoyable to play. However, redesigning these mini-games and implementing a launcher for the games has a high potential to improve their enjoyability by providing the aspects previously mentioned that define a desirable game.

\subsection{What is the problems context?}
Mini-Arcade is an application designed for anyone interested, regardless of the individuals' demographic characteristics. With the redesign of these simple games, we anticipate varying difficulty levels for players of different skill levels as well as a variety of mini-games to choose from to satisfy each individual's interests. This application is built for desktops with no specific hardware requirements. As many people have access to a computer, this creates an easily-accessible environment for our project, allowing anyone to utilize Mini-Arcade and have fun.

- A clear concise description of the issues that need to be addressed by your team
- What problem are you trying to solve? Not how you are going to solve the problem
- Why is this an important problem?
- What is the context of the problem you are solving?
	- Stakeholders?
	- Software environment?
	

%\wss{comment}

%\ds{comment}

%\mj{comment}

%\cm{comment}

%\mh{comment}

\end{document}
